\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2016-08-17 journalSwarmControl/relatedWork.tex
added ayanian

 \subsection{Human-swarm interaction}
\cite{Jr2004} studied human \emph{fanout}, the number of robots a single human user could control.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, our paper indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with 3 levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

\cite{Squire:2006:HCM:1121241.1121248} designed experiments showing user-interface design had a high impact on the task effectiveness and the number of robots that could be controlled simultaneously in a multi-robot task.

>>>>

 \subsection{Human-swarm interaction}

 \cite{ayanian2014controlling} designed a user interface enabling an operator to maneuver a swarm of robots through a cluttered workspace by specifying the bounding prism for the swarm and then translating or scaling this prism. Our paper shares the concept of a global control input, but our robots have no onboard computation and cannot track a virtual boundary.

\cite{Jr2004} studied human \emph{fanout}, the number of robots a single human user could directly control.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, our paper indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with 3 levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

%\cite{Squire:2006:HCM:1121241.1121248} designed experiments showing user-interface design had a high impact on the task effectiveness and the number of robots that could be controlled simultaneously in a multi-robot task.
